Approximation as Differentiation: Notes

### 2025-07-04 notes/predicate-system.tex
'Pred' not a category, so drop the bold..

>>>>

\subsubsection{Closure operator over a predicate system}

A \emph{closure operator} $C$ over a poset $X$ is a lax idempotent monad on $X$, with functoriality, unit and
multiplication given by monotonicity, extensivity ($x \leq C(x)$) and idempotence ($C(C(x)) \leq C(x)$).
Suppose $\mathcal{S} = (\Pred, \top, \meet, \join, \residual, \forall)$ a predicate system over a category
$\cat{C}$. A closure operator $C$ over $\mathcal{S}$ is a fibred lax idempotent monad $C$ on the fibration
$\Pred: \cat{C}^\op \to \Poset$ such that for every object $X$ in $\cat{C}$ the fibre map $\Pred(X)$ is a
closure operator, with a lax strength with respect to $\meet$.
